Assessing the Scientific Value of Amateur Photometric Observations of Binary Star Transits

### 2025-01-15 paper.tex
docs
Signed-off-by: Thomas Mauran <thomasmauran@yahoo.com>

\subsection{Figure 2}
One thing we see when looking at those light curves is the fact they are not overlapping. This can be explained by the fact that TESS is in space and doesn't have to deal with the atmosphere, making the star looks brighter. It could also be explained by the fact
TESS sensor is more sensitive than the one used in this study, making the star looks brighter. This is why the data is not overlapping, but the transit event is still clearly visible on both light curves.

@@

>>>>

\subsection{Figure 2}
One thing we see when looking at those light curves is the fact they are not overlapping. This can be explained because TESS is in space and doesn't have to deal with the atmosphere, making the star looks brighter. It could also be explained by the fact
TESS sensor is more sensitive than the one used in this study, making the star looks brighter. This is why the data is not overlapping, but the transit event is still clearly visible on both light curves.

@@

To have a better comparison I shifted the amateur data by -0.5, this way both light curves are overlapping. This shift allows us to see that the light curves are following the same path but that the amateur data is just a bit dimmer than the TESS data.
The variation of magnitude is different which is something I cannot explain. Even if my data is less precise in theory the variation of magnitude should be the same, but it is not the case here.

This might be explained by a difference of sensitivity of the sensors used, or by the fact that the data was not normalized correctly, but this is something that needs to be investigated further.
